brados: declarative, programmable object storage

### 2016-05-25 paper.tex
paper: fix sec3.2/3.3 links
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Figure~\ref{fig:vanilla_wr_jewel} shows the expected performance of 1K log
appends without metadata management overhead using each of the five strategies
defined in Table~\ref{tab:pd-map}. The first thing to notice in this figure is
that both one-to-one strategies have relatively poor performance. The large
period of reduced throughput for \emph{11wr} corresponds to the OSD splitting
file system directories in order to maintain a maximum directory size, and
will occur in \emph{11kv} although the threshold number of objects is not
reached in this example due to reduced overall throughput of the \emph{11kv}
strategy.

The second lesson that we can learn from Figure~\ref{fig:vanilla_wr_jewel} is
that even when using an N:1 addressing strategy, the key-value interface
imposes a large overhead. This is unfortunate because the key-value interface
can provide a direct solution to addressing log entries within an object.
Instead, what we find is that an N:1 addressing strategy that stores log
entries in the bytestream using either object appends or writes to explicit
offsets outperform all other strategies by a factor of over 2x.

@@

\begin{figure*}[t]
	\centering
	\includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/jewel_v_firefly_v_es.png}
	\caption{The cluster-specific optimizations impact performance... a lot. This caption is quite terrible.}
\end{figure*}

\begin{figure}[t]
      \centering
      \includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/output.read.60min.1k.png}
      \caption{This graph shows that a good choice for writes is also good for reads.}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=1.0\linewidth]{experiments/basic-cls-overhead/output.1024.soft.reset.png}
	\caption{1hr,1k,cls\_wr,jewel: this graph shows the overhead of class}
	\label{fig:cls_wr_jewel}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/jewel-hdd-128b.png}
	\caption{shows that with a HDD, it don't matter if you choose omap!!!!!}
	\label{fig:cls_wr_jewel}
\end{figure}
%\begin{figure}[t]
%  \centering
%  \begin{subfigure}[b]{.47\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{experiments/librados-sweep/jewel_ssd.png}
%      \caption{1hr,1k,wr,jewel}
%      \label{fig:vanilla_wr_jewel}
%  \end{subfigure}
%  \begin{subfigure}[b]{.47\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/output.read.60min.1k.png}
%      \caption{1hr,1k,rd,jewel}
%      \label{fig:vanilla_rd_jewel}
%  \end{subfigure}
%  \begin{subfigure}[b]{.47\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{experiments/basic-cls-overhead/output.1024.soft.reset.png}
%      \caption{1hr,1k,cls\_wr,jewel}
%      \label{fig:cls_wr_jewel}
%  \end{subfigure}
%  \begin{subfigure}[b]{.47\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{experiments/librados-sweep/firefly_ssd.png}
%      \caption{1hr,1k,wr,firefly}
%      \label{fig:vanilla_wr_firefly}
%  \end{subfigure}
%  \caption{placeholder.}
%\end{figure}

@@

@@

In this section we have demonstrated that a design based on an N:1 addressing
scheme that stores both log entries and metadata in the bytestream can provide
the best overall performance, and it does so by a large margin. However, this
process of design we have outlined may not yield such clear cut results when
applied in a different context. To illustrate the complexity and breadth of
this design space, we describe the software, system tunables, and hardware
parameters that affect the performance of ZLog.

@@

Ceph releases stable versions every year (Oct/Nov) and LTS versions every 3-4
months~\cite{website:ceph-releases}. The head of the master branch moves
quickly because there are over 400 contributors and an active mailing list.
Over the calendar year, there were between  70 and 260 commits per
week~\cite{website:ceph-github}. These releases contain performance fixes and
new features that could directly ZLog.

\textbf{Ceph Versions}: to show the affect that this has on ZLog's design, we
ran the same benchmark that measures expected append throughput shown in
Figure~\ref{fig:vanilla_wr_jewel} on identical hardware but instead use a
long-term support version of Ceph released two years ago. The result of this
benchmark is shown in Figure~\ref{fig:vanilla_wr_firefly} in which the
bytestream interface outperforms the key-value interface by 12\%, compared to
over 100\% in the newer version of Ceph. Qualitatively, given the reduced
overall throughput achieved in the older version, some developers may find that
incurring the overhead of using the key-value interface is an easy decision
given the reduced complexity of the design space for metadata management. If
this choice had been made, then a future system upgrade could drop a
significant number of iops on the floor.

>>>>

\begin{figure*}[t]
	\centering
	\includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/jewel_v_firefly_v_es.png}
	\caption{The cluster-specific optimizations impact performance... a lot. This caption is quite terrible.
	\label{fig:jewel_v_firefly_v_es}}
\end{figure*}

The top row of Figure~\ref{fig:jewel_v_firefly_v_es} shows the expected
performance of different sized log appends without metadata management overhead
using each of the five strategies defined in Table~\ref{tab:pd-map}.  Starting
with Jewel and 4KB entry sizes, we see that both one-to-one strategies have
relatively poor performance. Jewel with 1KB entry sizes sees a 2.5\(\times\)
performance increase for the N:1 KV mapping. The large period of reduced
throughput for corresponds to the OSD splitting file system directories in
order to maintain a maximum directory size, and will occur in \emph{1:1, KV}
although the threshold number of objects is not reached in this example due to
the reduced overall throughput of the \emph{1:1, KV} strategy.

The second lesson that we can learn from the Jewel row of
Figure~\ref{fig:jewel_v_firefly_v_es} is that even when using an N:1 addressing
strategy, the key-value interface imposes a large overhead. This is unfortunate
because the key-value interface can provide a direct solution to addressing log
entries within an object.  Instead, what we find is that an N:1 addressing
strategy that stores log entries in the bytestream using either object appends
or writes to explicit offsets outperform all other strategies by a factor of
over 2\(\times\).

\begin{figure}[t]
      \centering
      \includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/output.read.60min.1k.png}
      \caption{The expected random read performance from a log with 1KB entries
      performs best on the same strategy that the write performance performs
      best on - the N:1 bystream append strategy.}
      \label{fig:vanilla_rd_jewel}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/jewel-hdd-128b.png}
	\caption{shows that with a HDD, it don't matter if you choose omap!!!!!}
	\label{fig:cls_wr_jewel}
\end{figure}
%\begin{figure}[t]
%  \centering
%  \begin{subfigure}[b]{.47\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{experiments/librados-sweep/jewel_ssd.png}
%      \caption{1hr,1k,wr,jewel}
%      \label{fig:vanilla_wr_jewel}
%  \end{subfigure}
%  \begin{subfigure}[b]{.47\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/output.read.60min.1k.png}
%      \caption{1hr,1k,rd,jewel}
%      \label{fig:vanilla_rd_jewel}
%  \end{subfigure}
%  \begin{subfigure}[b]{.47\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{experiments/basic-cls-overhead/output.1024.soft.reset.png}
%      \caption{1hr,1k,cls\_wr,jewel}
%      \label{fig:cls_wr_jewel}
%  \end{subfigure}
%  \begin{subfigure}[b]{.47\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{experiments/librados-sweep/firefly_ssd.png}
%      \caption{1hr,1k,wr,firefly}
%      \label{fig:vanilla_wr_firefly}
%  \end{subfigure}
%  \caption{placeholder.}
%\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=1.0\linewidth]{experiments/basic-cls-overhead/output.1024.soft.reset.png}
	\caption{1hr,1k,cls\_wr,jewel: this graph shows the overhead of class}
	\label{fig:cls_wr_jewel}
\end{figure}

@@

In this section we have demonstrated that a design based on an N:1 addressing
scheme that stores both log entries and metadata in the bytestream can provide
the best overall performance, and it does so by a large margin. However, this
process of design we have outlined may not yield such clear cut results when
applied in a different context. To illustrate these contexts, we describe the 
software, system tunables, and hardware parameters that affect the performance 
of ZLog.

@@

Ceph releases stable versions every year (Oct/Nov) and LTS versions every 3-4
months~\cite{website:ceph-releases}. The head of the master branch moves
quickly because there are over 400 contributors and an active mailing list.
Over the past calendar year, there were between 70 and 260 commits per
week~\cite{website:ceph-github}.

\textbf{Ceph Versions}: to show the evolution of Ceph's performance and
behavior, we ran the same benchmark, which measures append throughput, with the
same configurations, hardware, and tunables on 2 versions of Ceph: Jewel (April
2016) - the newest stable release and Firefly (May 2014)- long term support
version that introduced cache tiering and erasure coding.
Figure~\ref{fig:jewel_v_firefly_v_es} shows the behavior and performance of the
benchmark for 128b, 1KB, and 4KB objects.

For all graphs,

That figure demonstrates that the 
bytestream interface outperforms the key-value interface by 12\%, compared to
over 100\% in the newer version of Ceph. Qualitatively, given the reduced
overall throughput achieved in the older version, some developers may find that
incurring the overhead of using the key-value interface is an easy decision
given the reduced complexity of the design space for metadata management. If
this choice had been made, then a future system upgrade could drop a
significant number of iops on the floor.
